---
output: html_document
---
<link rel="stylesheet" href="https://maxcdn.bootstrapcdn.com/bootstrap/3.3.7/css/bootstrap.min.css">
<style> 
  .right{ 
    float: right; 
  } 
  
  img{ 
    display:block; 
    margin: 0 auto;
  } 
  
  pre{ 
    overflow-x: hidden; 
    overflow-y: hidden; 
  } 
  
  body{ 
    margin-top: 20px; 
    margin-bottom: 20px; 
  } 
  
  .col-left{ 
    float: left; 
    width: 50%; 
  } 
  
  .col-right{ 
    float: right; 
    width: 50%; 
  } 
  
  p{
    margin-bottom: 0px;
  }
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
library(tidyverse)
library(RMySQL)
library(tidyverse)
library(likert)
library(ggplot2)
mydb <- dbConnect(MySQL(), user='root', password='cosmic joke', dbname='week2assignment', host='localhost')
```

<div class='jumbotron'>
  <h2 class='display-3 text-uppercase'>week 2 Assignment</h2>
  <h4 class='right text-uppercase'>By Brian Weinfeld</h4>
  <div class='clearfix'></div>
  <h5 class='right text-uppercase'>February 8, 2018</h5>
</div>

<div class='page-header text-uppercase'>
  <h3>What do my students think of the top grossing films of 2017?</h3>
</div>

<div class='well'>
  All of my students filled out a Google form asking them to rate each of the 6 highest grossing movies of 2017 on a scale from 0-5 based on how much they enjoyed the film. 0 was used to indicate the student had not seen the movie as Google forms did not appear to have an N/A option. The data was stored and downloaded in a csv file. A few lines are reproduced below.
</div>

<table class='table table-striped table-bordered'>
<thead>
<tr>
<th>
  Timestamp
</th>
<th>
  Email Address
</th>
<th>
  Star wars: The Last Jedi
</th>
<th>
  Beauty and the Beast (2017)
</th>
<th>
  Wonder Woman
</th>
<th>
  Guardians of the Galaxy vol. 2
</th>
<th>
  Jumanji: Welcome to the Jungle
</th>
<th>
  Spider-Man: Homecoming
</th>
</tr>
</thead>
<tbody>
<tr>
<td>2/5/2018 7:25:53</td>
<td>Redacted Unique 1</td>
<td>3</td>
<td>1</td>
<td>2</td>
<td>3</td>
<td>3</td>
<td>4</td>
</tr>
<tr>
<td>2/5/2018 7:27:25</td>
<td>Redacted Unique 2</td>
<td>5</td>
<td>4</td>
<td>0</td>
<td>0</td>
<td>5</td>
<td>0</td>
</tr>
<tr>
<td>2/5/2018 7:43:56</td>
<td>Redacted Unique 3</td>
<td>5</td>
<td>0</td>
<td>0</td>
<td>5</td>
<td>0</td>
<td>5</td>
</tr>
</tbody>
</table>

<div class='well'>
  I wrote an sql script to import the csv file into a table called ratings. The script is recreated below. This script removes the unneeded columns representing the timestamp and the email address and replaces all 0s with Null.
</div>

<pre>
DROP TABLE IF EXISTS ratings;

CREATE TABLE ratings(
 rating_id INTEGER AUTO_INCREMENT PRIMARY KEY NOT NULL,
 star_wars INTEGER,
 beauty_and_the_beast INTEGER,
 wonder_woman INTEGER,
 guardians_of_the_galaxy_2 INTEGER,
 jumanji INTEGER,
 spiderman_homecoming INTEGER
);

LOAD DATA LOCAL INFILE 'FILEPATHWAY' 
INTO TABLE ratings
FIELDS TERMINATED BY ',' 
ENCLOSED BY '"'
LINES TERMINATED BY '\n'
IGNORE 1 ROWS(@dummy, @dummy, @star_wars, @beauty_and_the_beast, @wonder_woman, @guardians_of_the_galaxy_2, @jumanji, @spiderman_homecoming)
SET
star_wars = nullif(@star_wars,0),
beauty_and_the_beast = nullif(@beauty_and_the_beast,0),
wonder_woman = nullif(@wonder_woman,0),
guardians_of_the_galaxy_2 = nullif(@guardians_of_the_galaxy_2,0),
jumanji = nullif(@jumanji,0),
spiderman_homecoming = nullif(@spiderman_homecoming,0)
;
</pre>

<div class='well'>
  Using the RMySQL library, I connected to the database and read the information into R. The primary key column was discarded and the columns were given names more appropriate for being displayed on plots.
</div>

```{r}
#mydb <- dbConnect(MySQL(), user='root', password='SECRET', dbname='week2assignment', host='localhost')
rb <- dbSendQuery(mydb, 'SELECT * FROM ratings')
data <- fetch(rb, n=-1) %>%
  subset(select=c(2:7))
colnames(data) <- lapply(names(data), FUN=function(x){gsub('_', ' ', x) %>% toupper()})
str(data)
```

<div class='well'>
  I decided to create a heat plot of the student's rankings using the likert library. This required processing the data to convert it to a factor all of which needed the same number of levels.
</div>

```{r}
#From Likert Demo
for(i in seq_along(data)) {
  data[,i] <- factor(data[,i], levels=1:5)
}
plot(likert(data), type='heat',low.color='white', high.color='red',text.color='black')
```

<div class='well'>
  I wanted to have a total count of each response (including N/A) so I created a new data frame that summarized this information.
</div>

```{r}
moded <- data.frame(t(rbind(apply(data, 2, FUN=function(x){table(factor(x, levels=1:5), useNA = 'always')}))))
rownames(moded) <- lapply(names(data), FUN=function(x){gsub('_', ' ', x) %>% toupper()})
colnames(moded) <- c(1:5, 'Not Seen')
moded
```

<div class='well'>
  Finally, I used the new data frame to display the proportion of students who had seen each movie.
</div>

```{r}
setNames(data.frame(rownames(moded), apply(moded, 1, FUN=function(x){ sum(x[1:5])/sum(x) })), c('Movie', 'Proportion')) %>%
  ggplot(aes(x=Movie, y=Proportion, fill=Movie)) + geom_bar(stat='identity') + theme(legend.position='none') + labs(title='Proportion of Students Who Saw Movie') + coord_flip()
```

<div class='alert alert-success'>
  Amongst my high school students, the most popular of the top 6 films of 2017 was Spider-Man: Homecoming while the most viewed was Guardians of the Galaxy 2. Unsurprisingly, the least liked movie and 2nd to least viewed was Beauty and the Beast, a movie whose target demographic consisted of families with younger children.
</div>



























